Guarded Recursive Type Theory via Sized Types

### 2018-12-19 code-oneclock-paper/latex/paper.tex
experiments with literate Agda

\DeclareUnicodeCharacter{931}{$\Sigma$}
\DeclareUnicodeCharacter{948}{$\delta$}
\DeclareUnicodeCharacter{957}{$\nu$}
\DeclareUnicodeCharacter{8718}{$\blacksquare$}
\DeclareUnicodeCharacter{8759}{::}
\DeclareUnicodeCharacter{9659}{$\vartriangleright$}

@@

@@

\section{Preliminaries}
\input{Prelude/Basics}
\input{Presheaves/Presheaves}
\input{Presheaves/Const}
\input{Presheaves/Terminal}
\input{Presheaves/Product}
\input{Presheaves/Sum}
\input{Presheaves/Exp}
\input{CloTT/Structure/Contexts}
\input{CloTT/Structure/Types}
\input{CloTT/Structure/Terms}
\input{CloTT/Structure/DefinitionalEquality}
\input{CloTT/Structure/ContextOperations}
\input{CloTT/Structure/Subst}
\input{CloTT/TypeFormers/UnitType}
\input{CloTT/TypeFormers/SumType}
\input{CloTT/TypeFormers/ProductType}
\input{CloTT/TypeFormers/FunctionType}
\input{CloTT/TypeFormers/ClockQuantification}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/LaterType}
\input{CloTT/TypeFormers/WeakenClock}
\input{CloTT/TypeFormers/Fix}
\input{CloTT/TypeFormers/Force}

\subsection{Sized Types}

@@

@@

\subsection{Clock Contexts}

\subsection{Presheaves}

@@

>>>>

\DeclareUnicodeCharacter{915}{$\Gamma$}
\DeclareUnicodeCharacter{931}{$\Sigma$}
\DeclareUnicodeCharacter{948}{$\delta$}
\DeclareUnicodeCharacter{957}{$\nu$}
\DeclareUnicodeCharacter{8718}{$\blacksquare$}
\DeclareUnicodeCharacter{8759}{::}
\DeclareUnicodeCharacter{9659}{$\vartriangleright$}

@@

% New commands for Agda inline code
\newcommand{\D}{\AgdaDatatype}
\newcommand{\IC}{\AgdaInductiveConstructor}
\newcommand{\F}{\AgdaFunction}
\newcommand{\Ar}{\AgdaArgument}
\newcommand{\Fi}{\AgdaField}

@@

\section{Preliminaries}
%% \input{Prelude/Basics}
%% \input{Presheaves/Presheaves}
%% \input{Presheaves/Const}
%% \input{Presheaves/Terminal}
%% \input{Presheaves/Product}
%% \input{Presheaves/Sum}
%% \input{Presheaves/Exp}
%% \input{CloTT/Structure/Contexts}
%% \input{CloTT/Structure/Types}
%% \input{CloTT/Structure/Terms}
%% \input{CloTT/Structure/DefinitionalEquality}
%% \input{CloTT/Structure/ContextOperations}
%% \input{CloTT/Structure/Subst}
%% \input{CloTT/TypeFormers/UnitType}
%% \input{CloTT/TypeFormers/SumType}
%% \input{CloTT/TypeFormers/ProductType}
%% \input{CloTT/TypeFormers/FunctionType}
%% \input{CloTT/TypeFormers/ClockQuantification}
%% \input{CloTT/TypeFormers/Later}
%% \input{CloTT/TypeFormers/LaterType}
%% \input{CloTT/TypeFormers/WeakenClock}
%% \input{CloTT/TypeFormers/Fix}
%% \input{CloTT/TypeFormers/Force}

%% \input{allcode}
\subsection{Sized Types}

@@

\section{Presheaves}

A presheaf is a functor from the category of sizes to \D{Set}.

\input{Presheaves/Presheaves}

Every type \Ar{A} in \D{Set} defines a constant presheaf whose action
on \Ar{i} is given by \Ar{A}, for any size \Ar{i}.
\input{Presheaves/Const}

Presheaves are the objects of a category whose morphisms are natural
transformations. This is a cartesian closed category with finite
coproducts.
The terminal object is the constant presheaf on the unit type \D{⊤},
i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Product}
%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
Coproducts are also defined in a similar pointwise way.

Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
 The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Exp}

@@

@@

A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

\input{CloTT/Structure/Contexts}

Since we are modeling a simply typed calculus, types are interpreted
in the same ways as contexts.

\input{CloTT/Structure/Types}

In \IC{set}, a term of type \Ar{A} in context \Ar{Γ} is a function
from \Ar{Γ} to \Ar{A}. In \IC{tot}, a term of type \Ar{A} in context
\Ar{Γ} is a natural transformation between the presheaves \Ar{Γ} and
\Ar{A}.

\input{CloTT/Structure/Terms}

Two types in \IC{set} are judgementally equal if and only if they are
isomorphic as elements of \D{Set}. Two types in \IC{tot} are
judgementally equal if and only if they are isomorphic as elements of
\D{PSh}.

Two terms in \IC{set} are judgementally equal if and only if they are
propositionally equal as functions. Two terms in \IC{tot} are
judgementally equal if and only if they are propositionally equal as
natural transformations.

\input{CloTT/Structure/DefinitionalEquality}
